---
title: "Data_Visualitation_TradeElasticities"
author: "Afonso Amaral"
date: "2023-09-05"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The input of this document is the output from the cleaned BACI dataset fitted to our purposes. The sub-dataset contemplating all of the imports arising from China, United States and United Kingdom we examine the change over time of trade from China, UK, and US, to the European Member-States yearly.

Importing the relevant libraries and colour palletes.
```{r Libraries, include = FALSE}
library(tidyverse)
library(RColorBrewer)
library(readxl)
library(lubridate)
library(patchwork)
library(gridExtra)
library(haven)
#library(wesanderson)

library(RColorBrewer)

colors_set3 <- brewer.pal(n = 12, name = "Set3")

#If necessary, here is the code to output a PDF using the library: Tinytex
#tinytex::install_tinytex()
```

Set directory to meet data set.

```{r, include = FALSE}
setwd("/Users/afonso/Library/CloudStorage/Box-Box/Afonso Research/2nd Part/Programing/TradeElasticities/Fontaigne_work")
```

Importing data from previous data cleaning part of the project. File "Tariff-line Trade Elasticities.Rmd".

```{r, include = FALSE}
Trade_EU_MainPartners_BACI_COVID <- readRDS("/Users/afonso/Library/CloudStorage/Box-Box/Afonso Research/2nd Part/Programing/TradeElasticities/Fontaigne_work/Data_Cleaning_Trade_COVID.rds")

#Separating between US, UK, CN
Trade_EU_MainPartners_BACI_COVID_CN <- Trade_EU_MainPartners_BACI_COVID[str_detect(Trade_EU_MainPartners_BACI_COVID$i, "156"), ]
Trade_EU_MainPartners_BACI_COVID_US <- Trade_EU_MainPartners_BACI_COVID[str_detect(Trade_EU_MainPartners_BACI_COVID$i, "842"), ]
Trade_EU_MainPartners_BACI_COVID_UK <- Trade_EU_MainPartners_BACI_COVID[str_detect(Trade_EU_MainPartners_BACI_COVID$i, "826"), ]
```

Making sure we are tracking the EU countries.
```{r}
EU_Countries <- c("Austria", "Belgium", "Bulgaria", "Croatia", "Cyprus", "Czechia", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Ireland", "Italy", "Latvia", "Lithuania", "Luxembourg", "Malta", "Netherlands", "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", "Sweden")
EU_Country_codes_only <- c("40", "56", "100", "191", "196", "203", "208", "233", "246", "251", "276", "300", "348", "372", "380", "428", "440", "442", "470", "528", "616", "620", "642", "703", "705", "724", "752")

EU_Country_codes <- data.frame(Countries = EU_Countries, Codes = EU_Country_codes_only)

#Lets create a function to find the codes or countries and vice versa:

get_country_or_code <- function(input) {
  # Check if the input is a country name
  if (input %in% EU_Country_codes$Countries) {
    return(EU_Country_codes$Codes[EU_Country_codes$Countries == input])
  }
  # Check if the input is a country code
  else if (input %in% EU_Country_codes$Codes) {
    return(EU_Country_codes$Countries[EU_Country_codes$Codes == input])
  }
  # If the input doesn't match any country name or code
  else {
    return("Invalid input")
  }
}
```


#### Chinese Imports to the European Union Member-states from 2018 to 2021

```{r, fig.width = 12, fig.height = 6}
Trade_EU_MainPartners_BACI_COVID_CN$k <- as.factor(Trade_EU_MainPartners_BACI_COVID_CN$k)

#Austria
Trade_EU_MainPartners_BACI_COVID_CN_AT_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Austria")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Austria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_AT_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Austria")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Austria"), sep = " ") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_AT_val + Trade_EU_MainPartners_BACI_COVID_CN_AT_q

#Belgium
Trade_EU_MainPartners_BACI_COVID_CN_BE_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Belgium"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_BE_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Belgium"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_BE_val + Trade_EU_MainPartners_BACI_COVID_CN_BE_q

#Bulgaria
Trade_EU_MainPartners_BACI_COVID_CN_BG_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Bulgaria")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Bulgaria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_BG_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Bulgaria")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Bulgaria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_BG_val + Trade_EU_MainPartners_BACI_COVID_CN_BG_q

#Croatia
Trade_EU_MainPartners_BACI_COVID_CN_HR_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Croatia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Croatia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_HR_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Croatia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Croatia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_HR_val + Trade_EU_MainPartners_BACI_COVID_CN_HR_q

#Cyprus
Trade_EU_MainPartners_BACI_COVID_CN_CY_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Cyprus")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Cyprus"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_CY_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Cyprus")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Cyprus"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_CY_val + Trade_EU_MainPartners_BACI_COVID_CN_CY_q

#Czechia
Trade_EU_MainPartners_BACI_COVID_CN_CZ_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Czechia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Czechia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_CZ_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Czechia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_CZ_val + Trade_EU_MainPartners_BACI_COVID_CN_CZ_q

#Denmark
Trade_EU_MainPartners_BACI_COVID_CN_DK_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Denmark")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Denmark"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_DK_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Denmark")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Denmark"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_DK_val + Trade_EU_MainPartners_BACI_COVID_CN_DK_q

#Estonia
Trade_EU_MainPartners_BACI_COVID_CN_EE_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Estonia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Estonia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_EE_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Estonia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Estonia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_EE_val + Trade_EU_MainPartners_BACI_COVID_CN_EE_q

#Finland
Trade_EU_MainPartners_BACI_COVID_CN_FL_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Finland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Finland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_FL_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Finland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Finland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_FL_val + Trade_EU_MainPartners_BACI_COVID_CN_FL_q

#France
Trade_EU_MainPartners_BACI_COVID_CN_FR_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("France")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to France"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_FR_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("France")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to France"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_FR_val + Trade_EU_MainPartners_BACI_COVID_CN_FR_q

#Germany
Trade_EU_MainPartners_BACI_COVID_CN_DE_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Germany")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Germany"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_DE_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Germany")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Germany"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_DE_val + Trade_EU_MainPartners_BACI_COVID_CN_DE_q

#Greece
Trade_EU_MainPartners_BACI_COVID_CN_GR_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Greece")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Greece"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_GR_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Greece")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Greece"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_GR_val + Trade_EU_MainPartners_BACI_COVID_CN_GR_q

#Hungary
Trade_EU_MainPartners_BACI_COVID_CN_HU_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Hungary")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Hungary"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_HU_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Hungary")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Hungary"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_HU_val + Trade_EU_MainPartners_BACI_COVID_CN_HU_q

#Ireland
Trade_EU_MainPartners_BACI_COVID_CN_IE_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Ireland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Ireland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_IE_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Ireland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Ireland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_IE_val + Trade_EU_MainPartners_BACI_COVID_CN_IE_q

#Italy
Trade_EU_MainPartners_BACI_COVID_CN_IT_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Italy")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Italy"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_IT_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Italy")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Italy"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_IT_val + Trade_EU_MainPartners_BACI_COVID_CN_IT_q

#Latvia
Trade_EU_MainPartners_BACI_COVID_CN_LV_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Latvia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Latvia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_LV_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Latvia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Latvia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_LV_val + Trade_EU_MainPartners_BACI_COVID_CN_LV_q

#Lithuania
Trade_EU_MainPartners_BACI_COVID_CN_LT_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Lithuania")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Lithuania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_LT_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Lithuania")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Lithuania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_LT_val + Trade_EU_MainPartners_BACI_COVID_CN_LT_q

#Luxembourg
Trade_EU_MainPartners_BACI_COVID_CN_LU_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Luxembourg")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Luxembourg"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_LU_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Luxembourg")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Luxembourg"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_LU_val + Trade_EU_MainPartners_BACI_COVID_CN_LU_q

#Malta
Trade_EU_MainPartners_BACI_COVID_CN_MT_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Malta")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Malta"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_MT_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Malta")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Malta"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_MT_val + Trade_EU_MainPartners_BACI_COVID_CN_MT_q

#Netherlands
Trade_EU_MainPartners_BACI_COVID_CN_NE_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Netherlands")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Netherlands"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_NE_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Netherlands")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Netherlands"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_NE_val + Trade_EU_MainPartners_BACI_COVID_CN_NE_q

#Poland
Trade_EU_MainPartners_BACI_COVID_CN_PL_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Poland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Poland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_PL_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Poland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Poland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_PL_val + Trade_EU_MainPartners_BACI_COVID_CN_PL_q

#Portugal
Trade_EU_MainPartners_BACI_COVID_CN_PT_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Portugal")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Portugal"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_PT_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Portugal")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Portugal"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_PT_val + Trade_EU_MainPartners_BACI_COVID_CN_PT_q

#Romania
Trade_EU_MainPartners_BACI_COVID_CN_RO_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Romania")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Romania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_RO_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Romania")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Romania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_RO_val + Trade_EU_MainPartners_BACI_COVID_CN_RO_q

#Slovakia
Trade_EU_MainPartners_BACI_COVID_CN_SK_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Slovakia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Slovakia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_SK_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Slovakia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Slovakia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_SK_val + Trade_EU_MainPartners_BACI_COVID_CN_SK_q

#Slovenia
Trade_EU_MainPartners_BACI_COVID_CN_SL_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Slovenia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Slovenia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_SL_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Slovenia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Slovenia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_SL_val + Trade_EU_MainPartners_BACI_COVID_CN_SL_q

#Spain
Trade_EU_MainPartners_BACI_COVID_CN_ES_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Spain")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Spain"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_ES_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Spain")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Spain"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_ES_val + Trade_EU_MainPartners_BACI_COVID_CN_ES_q

#Sweden
Trade_EU_MainPartners_BACI_COVID_CN_SE_val <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Sweden")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from China to Sweden"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_CN_SE_q <- Trade_EU_MainPartners_BACI_COVID_CN %>% filter(j %in% get_country_or_code("Sweden")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from China to Sweden"), sep = " ") + theme_bw() + scale_color_brewer(palette = "Set3")

#Legend code: + theme(legend.position = "bottom") + guides(color = guide_legend(direction = "horizontal"))

Trade_EU_MainPartners_BACI_COVID_CN_SE_val + Trade_EU_MainPartners_BACI_COVID_CN_SE_q

```


#### Imports from United States to European Union Member-States from 2018 to 2021

```{r}
Trade_EU_MainPartners_BACI_COVID_US$k <- as.factor(Trade_EU_MainPartners_BACI_COVID_US$k)

#Austria
Trade_EU_MainPartners_BACI_COVID_US_AT_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Austria")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Austria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_AT_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Austria")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Austria"), sep = " ") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_AT_val + Trade_EU_MainPartners_BACI_COVID_US_AT_q

#Belgium
Trade_EU_MainPartners_BACI_COVID_US_BE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Belgium"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_BE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Belgium"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_BE_val + Trade_EU_MainPartners_BACI_COVID_US_BE_q

#Bulgaria
Trade_EU_MainPartners_BACI_COVID_US_BG_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Bulgaria")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Bulgaria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_BG_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Bulgaria")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Bulgaria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_BG_val + Trade_EU_MainPartners_BACI_COVID_US_BG_q

#Croatia
Trade_EU_MainPartners_BACI_COVID_US_HR_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Croatia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Croatia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_HR_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Croatia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Croatia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_HR_val + Trade_EU_MainPartners_BACI_COVID_US_HR_q

#Cyprus
Trade_EU_MainPartners_BACI_COVID_US_CY_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Cyprus")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Cyprus"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_CY_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Cyprus")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Cyprus"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_CY_val + Trade_EU_MainPartners_BACI_COVID_US_CY_q

#Czechia
Trade_EU_MainPartners_BACI_COVID_US_CZ_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Czechia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Czechia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_CZ_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Czechia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_CZ_val + Trade_EU_MainPartners_BACI_COVID_US_CZ_q

#Denmark
Trade_EU_MainPartners_BACI_COVID_US_DK_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Denmark")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Denmark"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_DK_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Denmark")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Denmark"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_DK_val + Trade_EU_MainPartners_BACI_COVID_US_DK_q

#Estonia
Trade_EU_MainPartners_BACI_COVID_US_EE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Estonia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Estonia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_EE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Estonia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Estonia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_EE_val + Trade_EU_MainPartners_BACI_COVID_US_EE_q

#Finland
Trade_EU_MainPartners_BACI_COVID_US_FL_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Finland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Finland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_FL_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Finland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Finland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_FL_val + Trade_EU_MainPartners_BACI_COVID_US_FL_q

#France
Trade_EU_MainPartners_BACI_COVID_US_FR_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("France")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to France"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_FR_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("France")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to France"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_FR_val + Trade_EU_MainPartners_BACI_COVID_US_FR_q

#Germany
Trade_EU_MainPartners_BACI_COVID_US_DE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Germany")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Germany"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_DE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Germany")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Germany"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_DE_val + Trade_EU_MainPartners_BACI_COVID_US_DE_q

#Greece
Trade_EU_MainPartners_BACI_COVID_US_GR_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Greece")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Greece"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_GR_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Greece")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Greece"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_GR_val + Trade_EU_MainPartners_BACI_COVID_US_GR_q

#Hungary
Trade_EU_MainPartners_BACI_COVID_US_HU_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Hungary")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Hungary"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_HU_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Hungary")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Hungary"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_HU_val + Trade_EU_MainPartners_BACI_COVID_US_HU_q

#Ireland
Trade_EU_MainPartners_BACI_COVID_US_IE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Ireland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Ireland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_IE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Ireland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Ireland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_IE_val + Trade_EU_MainPartners_BACI_COVID_US_IE_q

#Italy
Trade_EU_MainPartners_BACI_COVID_US_IT_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Italy")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Italy"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_IT_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Italy")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Italy"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_IT_val + Trade_EU_MainPartners_BACI_COVID_US_IT_q

#Latvia
Trade_EU_MainPartners_BACI_COVID_US_LV_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Latvia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Latvia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_LV_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Latvia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Latvia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_LV_val + Trade_EU_MainPartners_BACI_COVID_US_LV_q

#Lithuania
Trade_EU_MainPartners_BACI_COVID_US_LT_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Lithuania")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Lithuania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_LT_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Lithuania")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Lithuania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_LT_val + Trade_EU_MainPartners_BACI_COVID_US_LT_q

#Luxembourg
Trade_EU_MainPartners_BACI_COVID_US_LU_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Luxembourg")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Luxembourg"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_LU_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Luxembourg")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Luxembourg"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_LU_val + Trade_EU_MainPartners_BACI_COVID_US_LU_q

#Malta
Trade_EU_MainPartners_BACI_COVID_US_MT_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Malta")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Malta"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_MT_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Malta")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Malta"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_MT_val + Trade_EU_MainPartners_BACI_COVID_US_MT_q

#Netherlands
Trade_EU_MainPartners_BACI_COVID_US_NE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Netherlands")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Netherlands"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_NE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Netherlands")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Netherlands"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_NE_val + Trade_EU_MainPartners_BACI_COVID_US_NE_q

#Poland
Trade_EU_MainPartners_BACI_COVID_US_PL_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Poland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Poland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_PL_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Poland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Poland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_PL_val + Trade_EU_MainPartners_BACI_COVID_US_PL_q

#Portugal
Trade_EU_MainPartners_BACI_COVID_US_PT_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Portugal")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Portugal"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_PT_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Portugal")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Portugal"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_PT_val + Trade_EU_MainPartners_BACI_COVID_US_PT_q

#Romania
Trade_EU_MainPartners_BACI_COVID_US_RO_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Romania")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Romania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_RO_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Romania")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Romania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_RO_val + Trade_EU_MainPartners_BACI_COVID_US_RO_q

#Slovakia
Trade_EU_MainPartners_BACI_COVID_US_SK_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Slovakia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Slovakia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_SK_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Slovakia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Slovakia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_SK_val + Trade_EU_MainPartners_BACI_COVID_US_SK_q

#Slovenia
Trade_EU_MainPartners_BACI_COVID_US_SL_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Slovenia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Slovenia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_SL_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Slovenia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Slovenia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_SL_val + Trade_EU_MainPartners_BACI_COVID_US_SL_q

#Spain
Trade_EU_MainPartners_BACI_COVID_US_ES_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Spain")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Spain"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_ES_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Spain")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Spain"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_ES_val + Trade_EU_MainPartners_BACI_COVID_US_ES_q

#Sweden
Trade_EU_MainPartners_BACI_COVID_US_SE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Sweden")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from US to Sweden"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_SE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Sweden")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from US to Sweden"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_SE_val + Trade_EU_MainPartners_BACI_COVID_US_SE_q

```



#### Imports from United Kingdom to European Union Member-States from 2018 to 2021

```{r}
Trade_EU_MainPartners_BACI_COVID_UK$k <- as.factor(Trade_EU_MainPartners_BACI_COVID_UK$k)


#Austria
Trade_EU_MainPartners_BACI_COVID_UK_AT_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Austria")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Austria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_AT_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Austria")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Austria"), sep = " ") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_AT_val + Trade_EU_MainPartners_BACI_COVID_UK_AT_q

#Belgium
Trade_EU_MainPartners_BACI_COVID_UK_BE_val <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Belgium"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_BE_q <- Trade_EU_MainPartners_BACI_COVID_US %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Belgium"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_BE_val + Trade_EU_MainPartners_BACI_COVID_UK_BE_q

#Bulgaria
Trade_EU_MainPartners_BACI_COVID_UK_BG_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Bulgaria")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Bulgaria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_BG_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Bulgaria")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Bulgaria"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_BG_val + Trade_EU_MainPartners_BACI_COVID_UK_BG_q

#Croatia
Trade_EU_MainPartners_BACI_COVID_UK_HR_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Croatia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Croatia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_HR_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Croatia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Croatia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_HR_val + Trade_EU_MainPartners_BACI_COVID_UK_HR_q

#Cyprus
Trade_EU_MainPartners_BACI_COVID_UK_CY_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Cyprus")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Cyprus"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_CY_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Cyprus")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Cyprus"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_CY_val + Trade_EU_MainPartners_BACI_COVID_UK_CY_q

#Czechia
Trade_EU_MainPartners_BACI_COVID_UK_CZ_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Czechia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Czechia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_CZ_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Belgium")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Czechia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_CZ_val + Trade_EU_MainPartners_BACI_COVID_UK_CZ_q

#Denmark
Trade_EU_MainPartners_BACI_COVID_UK_DK_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Denmark")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Denmark"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_DK_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Denmark")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Denmark"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_DK_val + Trade_EU_MainPartners_BACI_COVID_UK_DK_q

#Estonia
Trade_EU_MainPartners_BACI_COVID_UK_EE_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Estonia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Estonia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_EE_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Estonia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Estonia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_EE_val + Trade_EU_MainPartners_BACI_COVID_UK_EE_q

#Finland
Trade_EU_MainPartners_BACI_COVID_UK_FL_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Finland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Finland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_FL_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Finland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Finland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_FL_val + Trade_EU_MainPartners_BACI_COVID_UK_FL_q

#France
Trade_EU_MainPartners_BACI_COVID_UK_FR_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("France")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to France"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_FR_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("France")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to France"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_FR_val + Trade_EU_MainPartners_BACI_COVID_UK_FR_q

#Germany
Trade_EU_MainPartners_BACI_COVID_UK_DE_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Germany")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Germany"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_DE_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Germany")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Germany"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_DE_val + Trade_EU_MainPartners_BACI_COVID_UK_DE_q

#Greece
Trade_EU_MainPartners_BACI_COVID_UK_GR_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Greece")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Greece"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_GR_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Greece")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Greece"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_GR_val + Trade_EU_MainPartners_BACI_COVID_UK_GR_q

#Hungary
Trade_EU_MainPartners_BACI_COVID_UK_HU_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Hungary")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Hungary"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_HU_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Hungary")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Hungary"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_US_HU_val + Trade_EU_MainPartners_BACI_COVID_US_HU_q

#Ireland
Trade_EU_MainPartners_BACI_COVID_UK_IE_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Ireland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Ireland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_IE_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Ireland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Ireland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_IE_val + Trade_EU_MainPartners_BACI_COVID_UK_IE_q

#Italy
Trade_EU_MainPartners_BACI_COVID_UK_IT_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Italy")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Italy"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_IT_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Italy")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Italy"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_IT_val + Trade_EU_MainPartners_BACI_COVID_UK_IT_q

#Latvia
Trade_EU_MainPartners_BACI_COVID_UK_LV_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Latvia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Latvia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_LV_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Latvia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Latvia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_LV_val + Trade_EU_MainPartners_BACI_COVID_UK_LV_q

#Lithuania
Trade_EU_MainPartners_BACI_COVID_UK_LT_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Lithuania")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Lithuania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_LT_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Lithuania")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Lithuania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_LT_val + Trade_EU_MainPartners_BACI_COVID_UK_LT_q

#Luxembourg
Trade_EU_MainPartners_BACI_COVID_UK_LU_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Luxembourg")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Luxembourg"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_LU_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Luxembourg")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Luxembourg"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_LU_val + Trade_EU_MainPartners_BACI_COVID_UK_LU_q

#Malta
Trade_EU_MainPartners_BACI_COVID_UK_MT_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Malta")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Malta"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_MT_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Malta")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Malta"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_MT_val + Trade_EU_MainPartners_BACI_COVID_UK_MT_q

#Netherlands
Trade_EU_MainPartners_BACI_COVID_UK_NE_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Netherlands")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Netherlands"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_NE_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Netherlands")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Netherlands"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_NE_val + Trade_EU_MainPartners_BACI_COVID_UK_NE_q

#Poland
Trade_EU_MainPartners_BACI_COVID_UK_PL_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Poland")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Poland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_PL_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Poland")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Poland"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_PL_val + Trade_EU_MainPartners_BACI_COVID_UK_PL_q

#Portugal
Trade_EU_MainPartners_BACI_COVID_UK_PT_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Portugal")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Portugal"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_PT_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Portugal")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Portugal"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_PT_val + Trade_EU_MainPartners_BACI_COVID_UK_PT_q

#Romania
Trade_EU_MainPartners_BACI_COVID_UK_RO_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Romania")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Romania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_RO_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Romania")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Romania"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_RO_val + Trade_EU_MainPartners_BACI_COVID_UK_RO_q

#Slovakia
Trade_EU_MainPartners_BACI_COVID_UK_SK_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Slovakia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Slovakia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_SK_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Slovakia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Slovakia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_SK_val + Trade_EU_MainPartners_BACI_COVID_UK_SK_q

#Slovenia
Trade_EU_MainPartners_BACI_COVID_UK_SL_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Slovenia")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Slovenia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_SL_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Slovenia")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Slovenia"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_SL_val + Trade_EU_MainPartners_BACI_COVID_UK_SL_q

#Spain
Trade_EU_MainPartners_BACI_COVID_UK_ES_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Spain")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Spain"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_ES_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Spain")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Spain"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_ES_val + Trade_EU_MainPartners_BACI_COVID_UK_ES_q

#Sweden
Trade_EU_MainPartners_BACI_COVID_UK_SE_val <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Sweden")) %>% ggplot() + geom_line(aes(x = t, y = v, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Value(€) of COVID-19 relevant products from UK to Sweden"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_SE_q <- Trade_EU_MainPartners_BACI_COVID_UK %>% filter(j %in% get_country_or_code("Sweden")) %>% ggplot() + geom_line(aes(x = t, y = q, group = k, color = k), linewidth = 1.1) + labs(title = paste("Imports Quantity (100Kg) of COVID-19 relevant products from UK to Sweden"), sep = " ") + guides(color = "none") + theme_bw() + scale_color_brewer(palette = "Set3")

Trade_EU_MainPartners_BACI_COVID_UK_SE_val + Trade_EU_MainPartners_BACI_COVID_UK_SE_q

```


After looking at these analysis per country per EU main trade partners, we should look into the different unit price payed by each country to China, US, and UK. And try to cluster it through either manufacturing capabilities or size of country. To be done:\

* Integrate all COVID-19 related products at the HS6 level. (In another document)
* Unit cost analysis per country (In this document);\
* Difference in increase of quantity imported. That is, how much each country relied on international trade to fulfill their internal demand;\
* Compare that with the internal production of Europe for each of these products (In a future document);\






